Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-20 paper.tex
tuner graph

>>>>

For some fabrication problems, the best material to assign to a location
depends on the material assignment at nearby locations. 
Tuning the free variables as if they were independent usually yields
unsatisfactory results.
Therefore, we allow the tuner to share information according to 
a user-specified graph structure. 
This allows our framework to be interfaced with a wide range of existing
graph based optimization and inference algorithms.
For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right). The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}.
\begin{figure}[h]
\includegraphics[scale=0.3]{figure/tuner.pdf}
\caption{A sample Tuner Graph for the Floyd–Steinberg dithering algorithm.}
\label{fig:tuner}
\end{figure}
